%-------------------------
% Rover Resume Template
% Link: https://github.com/subidit/rover-resume
%------------------------

\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{inter} % https://tug.org/FontCatalogue/
\renewcommand*\familydefault{\sfdefault}

\usepackage{geometry}
\geometry{
a4paper,
top=1.8cm,
bottom=1in,
left=2.5cm,
right=2.5cm
}

\setcounter{secnumdepth}{0} % remove section numbering
\pdfgentounicode=1 % make ATS friendly

% \usepackage[dvipsnames, svgnames, x11names]{xcolor} 
\usepackage[dvipsnames]{xcolor} % xcolor.pdf Sec.4 Colors by Name
\colorlet{icnclr}{gray}
% \colorlet [⟨type⟩]{⟨name⟩}[⟨num model⟩]{⟨color ⟩}
% \definecolor[⟨type⟩]{⟨name⟩}{⟨model-list⟩}{⟨spec-list⟩}

\usepackage{enumitem}
\setlist[itemize]{
    noitemsep,
    left=0pt..1.5em
}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left}

\usepackage{titlesec}
% \titlespacing{command}{left spacing}{before spacing}{after spacing}[right]
% \titlespacing{\section}{0pt}{*3}{*1}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
% \titleformat{<command>}[<shape>]{<format>}{<label>}{<sec>}{<before-code>}[<after-code>]  
\titleformat{\section}{\color{Sepia}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\large\fontseries{semibold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\large\fontseries{medium}\selectfont}{}{}{}

\usepackage{xhfill} 
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]} % add rule after title in .5 x-height 

\newif\ifRemVS % remove vspace between \section & \subsection
\newcommand{\rvs}{
    \ifRemVS
        \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}


\usepackage{fontawesome5}

\usepackage[bookmarks=false]{hyperref} % [imp!]
\hypersetup{ % https://en.wikibooks.org/wiki/LaTeX/Hyperlinks
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={Luqmanul Hakim - Resume},
}

\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}	
\fancyhf{}							
\cfoot{\color{darkgray} Yein Narayana Resume -- Page \thepage{} of \totalpages}


\begin{document}

%== HEADER ==%
\begin{center}
    {\fontsize{36}{36}\selectfont \interheavy Yein Narayana} \\ \bigskip
    {\color{gray}\fontsize{13}{13}\selectfont Frontend Engineer with 6+ year experiences} \\ \bigskip
    {\color{icnclr}\faEnvelope[regular]} \href{mailto:mrneverflatz@gmail.com}{mrneverflatz@gmail.com} $|$
    {\color{icnclr}\faIcon{mobile-alt}} \href{tel:+6281999620213}{+6281999620213}
    \\ {\color{icnclr}\faLinkedinIn} \href{https://www.linkedin.com/in/yein-narayana/}{linkedin/yein-narayana/}
\end{center}

\section{Professional Summary}
 {Frontend Engineer specialty in developing webapps interface to help end users get the best experience to simplify their daily jobs. With product mindset, I am able to build and passionate about business strategy to drive innovation through technology.}
%===============


\section{Experience}
%===================
\subsection{Mejadokter - Health Tech}
\subsubsection{CEO \& Founder | Oktober 2019 - Present \hfill Bali, Remote}
\begin{itemize}
    \item Tech Stack: Node.js, Express.js, Go, MongoDB, Redis, React
    \item Making sure Mejadokter's goals to transform health-care operations by digitizing medical data and clinical management systems. Leading the technology strategy and development, I am committed to producing solid digital solutions that improve operational efficiency and client satisfaction.
    \item Key achievements include:
          \begin{itemize}
              \item Implementation in a single medical facility begin from preparing master account, import database and system training.
              \item  Developed and implemented a strategic technology roadmap that includes major integrations such as Integrasi SatuSehat, Integrasi BPJS Antrian Online (aplikasi JKN), Integrasi BPJS Pcare, and a CRM system for patient management in clinics.
          \end{itemize}
\end{itemize}

\subsection{Buildwithangga - Edutech}
\subsubsection{Frontend Developer Mentor | May 2020 - Present \hfill Bandung, Remote}
\begin{itemize}
    \item Successfully publish several online class sharing about frontend development that helps people start their career as software engineer focus on frontend.
\end{itemize}

\subsection{AVANA - Social Commerce \& Web Builder}
\subsubsection{DevOps Engineer | Mar 2018 - Sep 2021 \hfill Malaysia, Remote}
\begin{itemize}
    \item Tech Stack: Reactjs, Nextjs
    \item At AVANA, Me and the team successfully migrate of our legacy dashboard and detach the main application from symphony (php framework) to single page application powered by reactjs.
\end{itemize}

\section{Skills}
%===============
\begin{description}
    \item[Technical] Node.js, MongoDB, Reactjs
    \item[Language] Bahasa Indonesia, English
        % \item[Laboratory] List scientific / research lab techniques or tools [If Applicable]
    \item[Interests] Software Engineering
\end{description}

% \section{Projects}
% %=================
% % \subsection{Project Name {\normalfont $|$ \href{http://github.com}{\textit{GitHub Link}}} \hfill 2022}
% \subsection{Siswamedia  \hfill 2022}
% \begin{itemize}
%     \item Tech Stack: Go, Flutter, MySQL, React
%     \item Implemented ABC feature
%     \item Optimised XYZ by 50\%
% \end{itemize}


% \section{Education}
%==============
% \vspace{0.5\baselineskip}

% \subsection{Asia Cyber University $|$ {\normalfont\textit{Bachelor of Accounting}} \hfill 2024 - On Going}
% \begin{itemize}
%     \item Cumulative GPA: 3.98
%     \item Related Coursework: Intro to Programming with Python, Database Administration
%     \item Rover Resume Award
% \end{itemize}

% \subsection{Graduation College \hfill City, State}
% \subsubsection{Degree Name (B.S.) \hfill Year}
% \begin{itemize}
%     \item GPA: 3.4 (Mention if good)
%     \item Related Coursework (list of relavent classes to the job)
%     \item Dean's Award (list any awards or a
%           +ivements)
% \end{itemize}
\vspace{0.5\baselineskip}

\end{document}